---
title: "Assignment 1"
output: 
  html_document:
    css: SLV_assignment1.css
---

<center>

Daniel Anadria, Kyuri Park, Ernst-Paul Swens, Emilia Loescher

</center>


# Loading the data and required packages
```{r}
library(dplyr)


housing <- read.csv("data/housing_data_italy_august2022.csv")

colnames(housing)
head(housing)
```

# Reducing/Modifying the data set
We need to modify the data to be able to work with it. 
For the visualization we have to create an "age" variable and exclude (?) housing units with a negative age (< -...).
Furthermore, 
For the second step, identifying the predictors, we need to exclude variables of class "character" and factors with more than 2 (3?) levels.  
```{r}
#Transforming "year_of_construction" in age (2022-year of construction) and removing "year_of_construction"
housing$age <- 2022 - as.numeric(housing$year_of_construction)
housing <- housing[, -10]

#Removing "status" (all "other") and "availability" (all "not free/other")
housing <- housing[, -c(10, 12)]


#DOES NOT WORK YET?!
housing[,11:22] <- apply(housing[,11:22], 2, as.factor)
summary(housing)

```



# Summary statistics 

# Visualization

# Exploring predictors for price
For the identification of predictors, we have to exclude some predictor such as ID and timestamp that do not make sense in this setting. Furthermore, in the first step, we exclude the location variable and identify a national prediction model.
```{r}
#For model building exclude the following variables:
colnames(housing)[-c(1:4)]
housing_red <- housing[,-c(1:4)]

head(housing_red)
```

## Backward selection

```{r}
#step(lm(price ~., housing_red), direction = backward)
```

## Forward selection

```{r}
#housing %>% step(lm(price ~., .), direction = forward)
```